%CV only relevant stuff... not full CV.

\chapter*{Curriculum Vitae}

\begin{table}[H]
\begin{tabular}{ll}
\textbf{Name:} & \firstname{} \lastname\\\\
\textbf{Post-Secondary}& M.Sc. in Biology\\
\textbf{Education and}& The University of Western Ontario\\
\textbf{Degrees:}& London, ON\\
& 2019 -- 2021\\\\
& B.Sc. (Hon.) in Genetics\\
& The University of Western Ontario\\
& London, ON\\
& 2014 -- 2019 \\\\
\textbf{Honours and}& Queen Elizabeth II Graduate Scholarship in Science\\
\textbf{Awards:}& and Technology (QEII-GSST)\\
& 2020 -- 2021\\\\
& Western Graduate Research Scholarship (WGRS)\\
& 2019 -- 2021\\\\
& Western Scholarship of Excellence\\
& 2014\\\\
\textbf{Related Work}& Biostatistics Teaching Assistant\\
\textbf{Experience:}& Department of Biology\\
& The University of Western Ontario\\
& 2019 -- 2021\\\\
& Undergraduate Research Assistant (Dr. Anne Simon)\\
& Department of Biology\\
& The University of Western Ontario\\
& 2018 -- 2019\\\\
& Bacteriology Technician (Dr. Edward Topp)\\
& Agriculture \& Agri-Food Canada\\
& 2017 -- 2018\\\\
\end{tabular}
\end{table}

\textbf{Publications:}\\
\begin{enumerate}
  \item{Yost, R. T., Robinson, J., Baxter, C. M., Scott, A. M., \textbf{Brown, L. P.}, Aletta, M., Hakimjavadi, R., Lone, A., Cumming, R. C., Dukas, R., Mozer, B., \& Simon, A. F. (2020). Abnormal social interactions in a \textit{Drosophila} mutant of an autism candidate gene: \textit{Neuroligin 3}. \textit{International Journal of Molecular Sciences}, \textit{21}(13), 4601. \url{https://doi.org/10.3390/ijms21134601}}
\end{enumerate}
\textbf{Conferences:}\\
\begin{enumerate}
  \item{\textbf{Poster}: Brown, L. P., Murray, R., Scott, A., Tien, Y.-C., Lau, C. H.-F., Tai, V., \& Topp, E. (2021). A decade of macrolide antibiotic exposure impacts the soil bacterial community, resistome, and mobilome. 70\textsuperscript{th} Annual Conference of the Canadian Society of Microbiologists (CSM 2021). Online.}
  \item{\textbf{Presentation (Keynote)}: Brown, L. P., Tai, V., Topp, E. (2021). The impact of long-term antibiotic exposure on soil bacteria: A human health perspective. Western Research Forum 2021. Online.}
  \item{\textbf{Poster}: Brown, L. P., Murray, R., Scott, A., \& Topp, E. (2019). Do benzalkonium chloride biocides promote antimicrobial resistance in environmental bacteria? 10\textsuperscript{th} Annual Biology Graduate Research Forum. Western University, London, ON.}
  \item{\textbf{Presentation}: Brown, L. P., Yost, R. T., \& Simon, A. F. (2019). Chasing the \textit{neuroligins}: Quantification of low copy transcripts in \textit{Drosophila melanogaster}. Ontario Biology Day 2019. Western University, London, ON.}
\end{enumerate}
